---
title: "Week 11 - Day 03 Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(factoextra)
library(cluster)
library(dendextend)
library(corrplot)
library(broom)

customers <- read_csv("data/mall_customers.csv")
```

1.
```{r}
head(customers)
```
```{r}
customers %>% 
  ggplot(aes(x = `Spending Score (1-100)`, y = `Annual Income (k$)`)) +
  geom_point()
```
 a lot of customers seem to be spread into around 5 groups
 
 High Income, High Spending
 Low Income, High Spending
 Mid Income, Mid Spending
 Low Income, Low Spending
 High Income, Low Spending
 
Some outliers, might need to be scaled?
Also columns are badly named

```{r}
customers <- customers %>% 
  janitor::clean_names() %>% 
  mutate(annual_income_scaled = scale(annual_income_k),
         spending_score_scaled = scale(spending_score_1_100)) %>% 
  select(spending_score_scaled, annual_income_scaled)
```

2.
```{r}
# clustered_customers <- customers %>% 
#   kmeans(centers = )
# no not yet
```

```{r}
max_k = 20

k_clusters <- k_clusters <- tibble(k = 1:max_k) %>% 
  mutate(kclust = map(k, ~kmeans(customers, centers = .x, nstart = 25)),
         glanced = map(kclust, glance),
         augmented = map(kclust, augment, customers))

customers_clusterers <- k_clusters %>% 
  unnest(glanced)
```

```{r}
customers_clusterers %>% 
  ggplot(aes(x = k,
             y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1, 20, 1))
```
 Checking another couple methods to make sure
```{r}
fviz_nbclust(customers,
             kmeans,
             method = "wss",
             nstart = 25)

fviz_nbclust(customers,
             kmeans,
             method = "silhouette",
             nstart = 25)
```
 
Looks like 5 clusters is optimal

3.
```{r}
customers_clusterers %>% 
  unnest(augmented) %>% 
  filter(k == 5) %>% 
  ggplot(aes(x = spending_score_scaled, y = annual_income_scaled, colour = .cluster)) +
  geom_point()
```

4.
Clustering may be appropriate, as there is definite groups within this data - Some are more spread out that others, but there is a pattern.

5.
Cluster 2 is the high income and high spending score cluster - These might be worth targetting for an advertising campaign, but seeing as they are already spending, it might not be quite as profitable than targetting another cluster. 

Cluster 4 is the mid range, average income, average spending. This might be a good target for marketting, as they are already spending, just not as much, and they have more income to fund said spending