---
title: "Week 1 Weekend Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggplot2)
books <- read_csv("data/books.csv")
```

```{r}
summary(books)
view(books)
```

Finding the average(mean and median) ratings of Star Trek books 
This method of filtering presents a potential problem - I potentially haven't identified all the Star Trek books, 
only the ones that happen to have Star Trek in the title. 
However, for the purposes of this homework, this will do.

```{r}


books_star_trek <- books %>%
 filter(grepl("Star Trek", title)) %>%
  mutate(mean_star_trek_rating = mean(average_rating),.after = average_rating,
         median_star_trek_rating = median(average_rating))

```


```{r}
# The below lines of code are not relevant - just checking that grepl functions 
# the way I think it does, and to see if I can identify any other books missed by
# my original filter
# --------------------------------------------------------------------
# books_next_generation <- books %>%
#   filter(grepl("next generation", title))
# books_deep_space_9 <- books %>%
#   filter(grepl("deep space", title))
# books_cat <- books %>% 
#   filter(grepl("cat", title))
```

 What's the difference between the mean and median ratings and the actual ratings?

```{r}
  

books_star_trek_averages <- books_star_trek %>% 
  mutate(ratings_diff_mean = case_when(
    average_rating > mean_star_trek_rating ~ "Greater than mean",
    average_rating <  mean_star_trek_rating  ~ "Lower than mean",
    TRUE ~ "Exactly Average"),
    .after = authors) %>% 
  mutate(ratings_diff_median = case_when(
    average_rating > median_star_trek_rating ~ "Greater than median",
    average_rating < median_star_trek_rating  ~ "Lower than median",
    TRUE ~ "Exactly Average")) 
books_star_trek_averages %>% 
 select(title, ratings_diff_median, ratings_diff_mean, average_rating)

# From these results, we can see that there are 7 books greater than the average rating, and 7 below.

  
```

I want to create scatter plot to show the rating of each book in the Star Trek data set against the number of pages.
In this scatter plot, i want to mark the mean rating and page numbers with lines.
Before i do this, i need to create an average_page_number column in my data-set 

```{r}

books_star_trek <- books_star_trek %>% 
  mutate(average_num_pages = mean(num_pages))

star_trek_page_ratings <- books_star_trek %>%
  ggplot(aes(x = num_pages, y = average_rating)) +
  geom_point()+
  geom_hline(yintercept = mean(books_star_trek$average_rating)) +
  geom_vline(xintercept = mean(books_star_trek$num_pages))

star_trek_page_ratings

books_star_trek %>% 
  select(title,mean_star_trek_rating, average_num_pages)

#-------------------------------------------------------------------------------
# This code results in an error - "Error in list2(...): object 'mean_star_trek_rating' not found. 

# The reason this isn't working is that the geom_hline and geom_vline functions are expecting 
# a single value, while I was trying to pass in an array of values. 

# To fix this, i could re-assign mean_star_trek_rating and average_num_pages to be single numbers
#   mean_star_trek_rating <- 3.725
#   average_num_pages <- 382.7857

# This means that my initial assumption, where i created an average_page_number
# column, was incorrect.

# books_star_trek %>%
#   ggplot(aes(x = num_pages, y = average_rating)) +
#   geom_point()+
#   geom_hline(yintercept = mean_star_trek_rating) +
#   geom_vline(xintercept = average_num_pages)
#-------------------------------------------------------------------------------
```

Out of curiousity, i decided to compare this spread to a similar graph depicting Agatha Christie novels. 
This is by no means a fair or meaningful comparison, but oh well

```{r}

books_mystery <- books %>% 
filter(grepl("Agatha Christie", authors))

mystery_page_ratings <- books_mystery %>% 
  ggplot(aes(x = num_pages, y = average_rating)) +
  geom_point()+
  geom_hline(yintercept = mean(books_mystery$average_rating)) +
  geom_vline(xintercept = mean(books_mystery$num_pages))

star_trek_page_ratings
mystery_page_ratings
```

mystery_page_ratings presents a new question - what are the lower to 0 page results?

```{r}
books_mystery %>% 
  filter(num_pages <= 100)

# This shows that a lot of the low page count books are audio books. This can be seen in the Publisher column - Does this apply to the original data set?

```

Using grepl, I am attempting to find how many books in the lower page counts are audio books 
This is assuming that low page count + the word "audio" in the publisher column means that it is an audio book.

```{r}
 

books %>% 
  filter(num_pages <= 100) %>% 
  mutate(audio = case_when(
    publisher = grepl("Audio", publisher) ~ "Audiobook",
    TRUE ~ "Not Audiobook"
  )) %>% 
  count(audio)
```

Going back to the original dataset, I want to find the highest rated book for each language code.

I have attempted to ignore values where the rating is 5, as my investigation suggests that
these ratings usually occur where there are very low numbers of ratings - Possibly only
one. 


```{r}

# Slice used to show top 2 ratings to check that code is indeed trying to ignore 5.0 ratings
books %>% 
  group_by(language_code) %>% 
  slice_max(average_rating != "5.0", n = 2, with_ties = FALSE) %>% 
  select(title, language_code, average_rating)
  

```

