---
title: "Week 2 - Day 2 - Homework"
output: html_notebook
---
```{r}
library(tidyverse)
tweets <- read.csv("data/code_clan_tweets.csv")
```

Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
head(tweets)
names(tweets)
```

Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. 
Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).

```{r}
tweets %>% 
  select(is_quote,favorite_count) %>% 
  mutate(favorite_quoted = case_when(
    is_quote == FALSE ~ favorite_count,
    is_quote == TRUE ~ 0)
  ) %>% 
  summarise(sum(favorite_quoted))
  
# 425 total
```

Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). 
Again, omit quoted tweets from the mean.

```{r}
tweets %>% 
  select(is_quote, retweet_count, source) %>% 
  mutate(retweet_quoted = case_when(
    is_quote == FALSE ~ retweet_count,
    is_quote == TRUE ~ 0)) %>% 
  group_by(source) %>% 
  summarise(mean(retweet_quoted))
```

Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. 
Assume that any tweets without a listed media type are of type “text”.

```{r}
tweets %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  select(favorite_count, media_type) %>% 
  group_by(media_type) %>% 
  summarise(sum(favorite_count))
```

Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
tweets %>% 
 mutate(mean_tweets = mean(display_text_width)) %>% 
  select(mean_tweets)

# 149.4188
```

Question 6.
The code_clan_info.csv data file contains status_url along with other info.
Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. 
Decide which variable to join the tibbles on.

```{r}
extra_data <- read.csv("data/code_clan_info.csv")

tweets_q6 <- tweets %>% 
  left_join(extra_data, by = "tweet_id")
```

Question 7.
From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. 
Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- tweets_q6 %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  drop_na()

codeclan_hashtags
```

Question 8.
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string.
Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases 
in which the hashtag string begins with characters c(.

```{r}
codeclan_hashtags %>% 
  mutate(multiple_hashtags = str_detect(hashtags, pattern = "[c]+[\\(]+"))
 
```

Question 9
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.
```{r}
tweets_q9 <- tweets %>% 
  mutate(text = str_to_lower(text)) %>% 
  mutate(is_edinburgh_here = str_detect(text, pattern = "edinburgh")) %>% 
  select(is_edinburgh_here) %>% 
  summarise(sum(is_edinburgh_here == TRUE))

tweets_q9
```

Question 10.
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.

```{r}
tweets %>% 
  mutate(tweeted_to = str_extract_all(text, pattern = "@+[A-Za-z0-9\\_]+"), .after = text) %>% 
  unnest_wider(tweeted_to, names_sep = "_") %>% 
  select(tweeted_to_1:tweeted_to_6)
 

```

 