---
title: "Week 6 - Weekend Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)

data("msleep")

view(msleep)
```
_______________________________
Question 2.
Jabberwockies sleep for around 7 hours a night, on average. 
Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

H0: mean_sleep_total == 7
Ha: mean_sleep_total != 7

significance level: 0.05


```{r}
# calculate mean_sleep_total
observed_stat_sleep <- msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))

observed_stat_sleep
```

```{r}
# generate NULL distribution
null_distribution_sleep <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 2000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution_sleep %>% 
  visualise(bins = 25) +
  shade_p_value(obs_stat = observed_stat_sleep,
                direction = "both")
```
```{r}
null_distribution_sleep %>% 
  get_p_value(obs_stat = observed_stat_sleep,
                direction = "both") %>% 
  pull() %>% 
  format.pval()
```
Given that the p-value is lower than the significance level (almost 0% against 5%), We may reject H0 in favour of the alternative hypothesis that the mean sleep total is different to that of the jabberwocky
_________________________________________
Question 3.
Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

H0: mean_sleep_total_omni >= mean_sleep_total_herb
Ha: mean_sleep_total_omni < mean_sleep_time_herb

significance level: 0.05

```{r}
# calculate mean_sleep_total for omnivores
observed_stat_sleep_omni <- msleep %>% 
  group_by(vore) %>% 
  summarise(mean_sleep_total = mean(sleep_total)) %>% 
  filter(vore == "omni") %>% 
  select(mean_sleep_total)

observed_stat_sleep_herbi <- msleep %>% 
  group_by(vore) %>% 
  summarise(mean_sleep_total = mean(sleep_total)) %>% 
  filter(vore == "herbi") %>% 
  select(mean_sleep_total)

observed_stat_sleep_omni
observed_stat_sleep_herbi
```
```{r}
# generate NULL distribution
null_distribution_sleep2 <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = observed_stat_sleep_herbi$mean_sleep_total) %>% 
  generate(reps = 2000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution_sleep2 %>% 
  visualise(bins = 25) +
  shade_p_value(obs_stat = observed_stat_sleep_omni,
                direction = "less")
```

```{r}
null_distribution_sleep %>% 
  get_p_value(obs_stat = observed_stat_sleep_omni,
                direction = "less")
```
Given that our p value is 1, which is higher than our significance level of 0.05, we cannot reject H0 

Question 4. 
Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.

H0: prop_domesticated <= 0.05
Ha: prop_domesticated > 5

```{r}

```

