---
title: "Day 2 Homework"
output: html_notebook
---


1) Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc.?
```{r}
library(CodeClanData)
library(tidyverse)
drinks_content

names(drinks_content)

dim(drinks_content)

glimpse(drinks_content)
```

2) Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.

```{r}
drinks_content %>% 
  select(Beverage_category, Beverage, Beverage_prep, Calories) #I didn't programmatically solve this - I just looked at the the data                                                                 to see that there were no NA values
```

3) Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract 135 from the calories to see which drink have more or less than 10 cups of sugar).

```{r}
drinks_content %>% 
  mutate(calorie_diff = Calories - 135,.after = Calories)
```

4) Summarise the mean number of calories in each beverage_category. Which 3 category of drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.

Summary : Smoothies, Frappuccino® Blended Coffee & Signature Espresso Drinks have the most Calories
        : Classic Espresso Drinks, Shaken Ice Beverages & Coffee have the least

```{r}
drinks_content %>% 
  group_by(Beverage_category) %>% 
   summarise(mean_calories = mean(Calories)) %>% 
    arrange(desc(mean_calories))
      
```

5) Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?
```{r}
drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories_prep = mean(Calories)) %>% 
  arrange(desc(mean_calories_prep))
```

6) Which Beverage_prep type contains more than the average calories of all drinks?
```{r}
drinks_content %>% 
  mutate(average_calories = mean(Calories)) %>%  #Average Calories = 193.8719 - Simplified to 194
    filter(Calories >= average_calories) %>% 
      group_by(Beverage_prep) %>% 
        summarise(Beverage_prep, count = n()) %>% #summarise(Beverage_prep.. - Beverage_prep is unnecessary here, and causes the                                                        summarise to not 'collapse'. It already knows to look at this variable due to the                                                     group_by
          arrange(desc(count))                  #This doesn't feel like the cleanest way to do this
```

7) Which is the best type of coffee drink (and by ‘drink’ we mean the combination of Beverage_category, Beverage and Beverage_prep) to get if you’re worried about consuming too many calories?

It seems that a Short Brewed Coffee has the lowest calorie count while still being a Coffee drink.
```{r}
drinks_content %>% 
  mutate(average_calories = mean(Calories)) %>%  #Average Calories = 193.8719 - Simplified to 194
    filter(Calories <= average_calories) %>% 
      summarise(Beverage_category, Beverage, Beverage_prep, Calories) %>% 
        arrange (desc(Calories)) %>% 
          tail (5)
```


