---
title: "Week 10 - Weekend Homework"
output: html_notebook
---
```{r}
library(tidyverse)
library(tidyverse)
library(modelr)
library(GGally)
library(ggfortify)
```

```{r}
red_wine <- read_csv("data/wine_quality_red.csv")
white_wine <- read_csv("data/wine_quality_white.csv")
```

```{r}
head(red_wine)
head(white_wine)
```
split into some groups to make the ggpair plot readable
"The classes are ordered and not balanced (e.g. there are many more normal wines than excellent or poor ones)."

# IMPORTANT: I don't know anything about Wine

```{r}
group_1 <- white_wine %>% 
  select(fixed_acidity:chlorides, quality)

group_2 <- white_wine %>% 
  select(free_sulfur_dioxide:region)
```




```{r message=FALSE, warning=FALSE}
group_1 %>% 
  ggpairs()

group_2 %>% 
  ggpairs()
```
group_1: chlorides and volatile_acidity might matter
group_2: Region might make a difference, as might alcohol.

```{r}
white_wine %>% 
  skimr::skim()

# lets try taking the log of the skewed things
white_wine_alt <- white_wine %>% 
  select(!c(wine_id, fixed_acidity, density, p_h, sulphates, alcohol, quality, region)) %>% 
  mutate(across(everything(), log)) %>%  
  rename_with(~ paste0("log_", .x)) %>% 
  bind_cols(white_wine)

group_3 <- white_wine_alt %>% 
  select(starts_with("log_"), quality)
```

```{r message=FALSE, warning=FALSE}
group_3 %>% 
  ggpairs()
```

```{r}
# Why is log_citric_acid broken

group_3 %>% 
  select(log_citric_acid) %>% 
  arrange(desc(log_citric_acid)) %>% 
  slice_tail(n = 10)

# oh
```
```{r}
group_3 <- group_3 %>% 
  select(!log_citric_acid)
```

Break down region into europe or not europe to see if that matters

```{r}
white_wine %>% 
  distinct(region)
  
white_wine_alt <- white_wine_alt %>% 
  mutate(europe = case_when(
    region == "Australia" ~ FALSE,
    region == "USA" ~ FALSE,
    TRUE ~ TRUE
    )) 

white_wine_alt %>% 
  select(region, europe, quality) %>% 
  ggpairs(aes(colour = region, alpha = 0.5))
```
Maybe it doesnt actually matter, but i'll try anyway

what about sweetness?

```{r message=FALSE, warning=FALSE}
white_wine_alt <- white_wine_alt %>% 
  # select(residual_sugar, quality) %>% 
  mutate(median_sugar = median(residual_sugar),
         mean_sugar = mean(residual_sugar),
         sugar_to_mean = case_when(
           residual_sugar > mean_sugar ~ "Greater",
           residual_sugar == mean_sugar ~ "The same",
           TRUE ~ "Lower"),
         sugar_to_median = case_when(
           residual_sugar > median_sugar ~ "Greater",
           residual_sugar == median_sugar ~ "The same",
           TRUE ~ "Lower")
         ) %>% 
  select(!c(mean_sugar, median_sugar)) 


white_wine_alt %>% 
  select(quality, residual_sugar, sugar_to_mean, sugar_to_median) %>% 
   ggpairs()

```

Looks like being more or less sugary than the average makes a sort of difference

```{r}
model_1a <- lm(
  formula = quality ~ alcohol,
  data = white_wine_alt
)

summary(model_1a)
autoplot(model_1a)
```

```{r}
model_1b <- lm(
  formula = quality ~ residual_sugar,
  data = white_wine_alt
)

model_1b_log <- lm(
  formula = quality ~ log_residual_sugar,
  data = white_wine_alt
)

model_1b_mean <- lm(
  formula = quality ~ sugar_to_mean,
  data = white_wine_alt
)

summary(model_1b)
autoplot(model_1b)

summary(model_1b_log)
autoplot(model_1b_log)

summary(model_1b_mean)
autoplot(model_1b_mean)

# Sweetness of a wine compared to average might make a difference
```
```{r}
model_1c <- lm(
  formula = quality ~ region,
  data = white_wine_alt
)

model_1c_alt <- lm(
  formula = quality ~ europe,
  data = white_wine_alt
)

summary(model_1c)
autoplot(model_1c)

summary(model_1c_alt)
autoplot(model_1c_alt)

# neither seem significant
```

```{r}
model_1d <- lm(
  formula = quality ~ chlorides,
  data = white_wine_alt
)

model_1d_log <- lm(
  formula = quality ~ log_chlorides,
  data = white_wine_alt
)

summary(model_1d)
autoplot(model_1d)

summary(model_1d_log)
autoplot(model_1d_log)

# Not a very high R-squared
```
```{r}
model_1e <- lm(
  formula = quality ~ volatile_acidity,
  data = white_wine_alt
)

summary(model_1e)
autoplot(model_1e)

```



gonna go with alcohol for model 1

```{r message=FALSE, warning=FALSE}
# I forgot about this step, so i went back and did it, but its too late to change all the stuff i've already done

white_wine_resid <- white_wine_alt %>% 
  add_residuals(model = model_1a) %>% 
  select(- c(quality, alcohol)) 

group_1_resid <- white_wine_resid %>% 
  select(!starts_with("log_")) %>% 
  select(!wine_id) %>% 
  select(fixed_acidity:total_sulfur_dioxide, resid)

group_2_resid <- white_wine_resid %>% 
  select(!starts_with("log_")) %>% 
  select(!wine_id) %>% 
  select(density:resid)

ggpairs(group_1_resid)
ggpairs(group_2_resid)
```


```{r}
model_2a <- lm(
  formula = quality ~ alcohol + region,
  data = white_wine_alt
)

summary(model_2a)
autoplot(model_2a)

model_2a_alt <- lm(
  formula = quality ~ alcohol + europe,
  data = white_wine_alt
)

summary(model_2a_alt)
autoplot(model_2a_alt)

# ok fine region doesnt make a significant difference
```
```{r}
model_2b <- lm(
  formula = quality ~ alcohol + p_h,
  data = white_wine_alt
)

summary(model_2b)
autoplot(model_2b)
```
```{r}
anova(model_1a, model_2b)
```

```{r}
model_2c <- lm(
  formula = quality ~ alcohol + sugar_to_mean,
  data = white_wine_alt
)

summary(model_2c)
autoplot(model_2c)
```
```{r}
anova(model_1a, model_2c)
```
seems to be more significant than ph. Let's go with that

```{r}
model_3a <- lm(
  formula = quality ~ alcohol + sugar_to_mean + p_h,
  data = white_wine_alt
)

summary(model_3a)
autoplot(model_3a)
```
```{r}
anova(model_1a, model_3a)
```

```{r message=FALSE, warning=FALSE}
white_wine_resid <- white_wine_alt %>% 
  add_residuals(model = model_3a) %>% 
  select(- c(quality, alcohol, sugar_to_mean, p_h, wine_id))

group_1_resid <- white_wine_resid %>% 
  select(!starts_with("log_")) %>% 
  select(fixed_acidity:total_sulfur_dioxide, resid)

group_2_resid <- white_wine_resid %>% 
  select(!starts_with("log_")) %>% 
  select(density:resid)

ggpairs(group_1_resid)
ggpairs(group_2_resid)
```
volatile_acidity might make a difference

```{r}
model_4a <- lm(
  formula = quality ~ alcohol + sugar_to_mean + p_h + volatile_acidity,
  data = white_wine_alt
)

summary(model_4a)
autoplot(model_4a)
```
```{r}
anova(model_3a, model_4a)
```
```{r}
broom::glance(model_3a)
print("gap") # just so i can tell which one is which 
broom::glance(model_4a)
```


## Interpretation 

It looks as if there is no one defining factor that makes a wine good - there doesn't seem to be a single variable that contributes to quality that much.
From my investigation, it seems that alcohol content, sweetness (defined by sugar content being above or below the mean), ph and the level of volatile acidity 
have some connection to quality. However, they only explain a small portion of the variance. 


Please note, this interpretation may be flawed in that I forgot to compare to the residuals until later. 