---
title: "Week2 Day1 Homework"
output: html_notebook
---
## 1.1 Joins

```{r}
library(tidyverse)
library(tidyr)
library(janitor)
card_base <- read.csv("data/CardBase.csv")
customer_base <- read.csv("data/CustomerBase.csv")
fraud_base <- read.csv("data/FraudBase.csv")
transaction_base <- read.csv("data/TransactionBase.csv")
```

Question 1

Read in all 4 credit card transaction datasets and clean column names

```{r}
clean_card_base <- card_base %>% 
  clean_names()
clean_customer_base <- customer_base %>% 
  clean_names()
clean_fraud_base <- fraud_base %>% 
  clean_names()
clean_transaction_base <- transaction_base %>% 
  clean_names()
```

Question 2

Join the data containing card details and customer details by customer id, so that all records of card details and any matching records in customer details are kept. Before you run the code, think about how many rows you expect to see after joining.

```{r}
card_customers <- left_join(clean_card_base, clean_customer_base, "cust_id")

card_customers

```

Question 3

Join the data containing fraud details with transaction details so all rows of both tables are kept. What does the resulting row number tell you?

```{r}
fraud_transactions <- full_join(clean_fraud_base, clean_transaction_base, "transaction_id")

fraud_transactions

# row number tells us all rows from transaction base have been added, with the fraud base rows being joined to the corresponding transaction_id's
```

Question 4

Join the data containing card details with transaction details so rows from the first which have matching ones in the second are returned, but only return rows in the first table once.

```{r}
card_transactions <- semi_join(clean_card_base, clean_transaction_base, c("card_number" = "credit_card_id"))

card_transactions
```

## 1.2 tidyr

Question 5

Read in hat_observations and separate observation into two columns, hat_colour and hat_type.

```{r}
hat <- read.csv("data/hat_observations.csv")
hat
```

```{r}
hat_separated <- hat %>% 
  separate(observation, c("hat_colour","hat_type"), sep = ",")

hat_separated
```

Question 6

Unite day, month, and year columns into a column called date using a suitable separator. Then find the date where the most berets were observed.

```{r}
hat_united <- hat_separated %>% 
  unite(date, c("day", "month", "year"), sep = "/")

hat_united 

hat_united %>% 
  arrange(desc(observation_count))
```

## 2: Extension
# 2.1 Joins

Can you join all 4 datasets together so that you’re left with a dataset that looks like below with 109 rows and 12 columns? 

```{r}
#start with making a full join of transaction and card bases
card_transactions_full <- full_join(clean_card_base, clean_transaction_base, c("card_number" = "credit_card_id"))

#card_transactions_full

#join card_transactions_full with customer base

card_customer_transactions <- full_join(card_transactions_full, clean_customer_base, "cust_id")

#card_customer_transactions

#now join all that with the fraud base in a big horrible variable name

fraud_card_customer_transactions <- left_join(clean_fraud_base, card_customer_transactions, "transaction_id")

fraud_card_customer_transactions
```

# 2.2 tidyr

Question 2

Read in exam_scores and transform it into long format with two new columns exam_question and score. Then, using separate and select, remove superfluous information from the values in exam_question

```{r}
exam_scores <- read.csv("data/exam_scores.csv")

# Use pivot_longer to put all the exam_Q columns into one column

exam_scores_longer <- exam_scores %>% 
  pivot_longer(cols = starts_with ("exam_Q"),
               names_to = "exam_question",
               values_to = "score")

exam_scores_longer

# Separate using separate to make columns containing only exam_Q and the number.
exam_score_separated <- exam_scores_longer %>% 
  separate(exam_question, c("filter_me", "exam_question"), sep = "exam_Q") %>% 
  select(id, exam_question, score)

exam_score_separated
```

