---
title: "Week 10 - Day 03 - Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(mosaic) 
library(janitor)
library(GGally) 
library(ggfortify)
library(modelr)
```

```{r}
housing_prices <- read_csv("data/kc_house_data.csv")

housing_prices
```
1.

```{r}
housing_prices_tidy <- housing_prices %>% 
  select(-c(id, date, zipcode, sqft_living15, sqft_lot15, lat, long)) %>%  # removing date as data only looks at one year - month to month changes are unlikely to be very drastic
  mutate(waterfront = as.logical(waterfront),
         renovated = case_when(
           yr_renovated == 0 ~ FALSE,
           TRUE ~ TRUE),
         grade = case_when(
           grade < 4 ~ "poor quality",
           grade == 4 ~ "below average",
           grade < 7 ~ "below average",
           grade == 7 ~ "average",
           grade < 11 ~ "above average",
           grade >= 11 ~ "high quality"
         ),
         basement = case_when(
           sqft_basement == 0 ~ FALSE,
           TRUE ~ TRUE
         ))  %>% 
  select(-yr_renovated, -sqft_basement)


housing_prices_tidy <- housing_prices_tidy %>% 
  select(-sqft_above)
# housing_prices %>% 
#   distinct(view)
# housing_prices %>% 
#   distinct(condition)

```
2.

```{r}
alias(lm(price ~ ., data = housing_prices_tidy))

# removed sqft_above in above chunk
```

3.

```{r message=FALSE, warning=FALSE}
housing_prices_numeric <- housing_prices_tidy %>%
  select_if(is.numeric)

housing_prices_nonnumeric <- housing_prices_tidy %>%
  select_if(function(x) !is.numeric(x))

housing_prices_nonnumeric <- housing_prices_nonnumeric %>% 
  mutate(price = housing_prices_tidy$price)

housing_prices_nonnumeric %>% 
  distinct(grade)
```


```{r message=FALSE, warning=FALSE}
ggpairs(housing_prices_numeric)
ggpairs(housing_prices_nonnumeric)
```
strong correlation between price ~ sqft_living, bathrooms
some correlation between price ~ bedrooms
waterfront, renovated and grade all seem to have a relationship with price

```{r}
price_sqft_living <- lm(
  formula = price ~ sqft_living,
  data = housing_prices_tidy
)


price_sqft_living  
```

```{r}
autoplot(price_sqft_living)
summary(price_sqft_living)
```
residuals vs fitted: some evidence of a pattern, skewed
normal Q-Q: somewhat follows line
scale-location: funneling, some heteroscedasticity

R^2 = 49%


```{r}
price_bathrooms <- lm(
  formula = price ~ bathrooms,
  data = housing_prices_tidy
)
```

```{r}
autoplot(price_bathrooms)
summary(price_bathrooms)
```
Plots look ok.

R^2 accounts for around 26% of variance


```{r}
autoplot(lm(
  formula = price ~ bedrooms,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ grade,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ floors,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ floors,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ waterfront,
  data = housing_prices_tidy
))


summary(lm(
  formula = price ~ waterfront,
  data = housing_prices_tidy
))
```

going with price_sqft_living

```{r}
housing_resid <- housing_prices_tidy %>% 
  add_residuals(model = price_sqft_living) %>% 
  select(-c(price, sqft_living))

housing_resid_numeric <- housing_resid %>%
  select_if(is.numeric)

housing_resid_nonnumeric <- housing_resid %>%
  select_if(function(x) !is.numeric(x))

housing_resid_nonnumeric <- housing_resid_nonnumeric %>% 
  mutate(resid = housing_resid$resid)
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_resid_numeric)
ggpairs(housing_resid_nonnumeric)
```
some relationship between residuals and waterfront, grade?

```{r}
autoplot(lm(
  formula = price ~ sqft_living + waterfront,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + waterfront,
  data = housing_prices_tidy
))
```
```{r}
autoplot(lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
))

price_living_grade <- lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
)
```

Going with grade, as it has a higher R^2

```{r}
anova(price_sqft_living, price_living_grade)
```

```{r}
housing_resid <- housing_prices_tidy %>% 
  add_residuals(model = price_living_grade) %>% 
  select(-c(price, sqft_living, grade))

housing_resid_numeric <- housing_resid %>%
  select_if(is.numeric)

housing_resid_nonnumeric <- housing_resid %>%
  select_if(function(x) !is.numeric(x))

housing_resid_nonnumeric <- housing_resid_nonnumeric %>% 
  mutate(resid = housing_resid$resid)
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_resid_numeric)
ggpairs(housing_resid_nonnumeric)
```
```{r}
autoplot(lm(
  formula = price ~ sqft_living + grade + waterfront,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + grade + waterfront,
  data = housing_prices_tidy
))
```

