---
title: "Week 10 - Day 03 - Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(mosaic) 
library(janitor)
library(GGally) 
library(ggfortify)
library(modelr)
```

```{r}
housing_prices <- read_csv("data/kc_house_data.csv")

housing_prices
```
1.

```{r}
housing_prices_tidy <- housing_prices %>% 
  select(-c(id, date, zipcode, sqft_living15, sqft_lot15, lat, long)) %>%  # removing date as data only looks at one year - month to month changes are unlikely to be very drastic
  mutate(waterfront = as.logical(waterfront),
         renovated = case_when(
           yr_renovated == 0 ~ FALSE,
           TRUE ~ TRUE),
         grade = case_when(
           grade < 4 ~ "poor quality",
           grade == 4 ~ "below average",
           grade < 7 ~ "below average",
           grade == 7 ~ "average",
           grade < 11 ~ "above average",
           grade >= 11 ~ "high quality"
         ),
         basement = case_when(
           sqft_basement == 0 ~ FALSE,
           TRUE ~ TRUE
         ))  %>% 
  select(-yr_renovated, -sqft_basement)


housing_prices_tidy <- housing_prices_tidy %>% 
  select(-sqft_above)
# housing_prices %>% 
#   distinct(view)
# housing_prices %>% 
#   distinct(condition)

```
2.

```{r}
alias(lm(price ~ ., data = housing_prices_tidy))

# removed sqft_above in above chunk
```

3.

```{r message=FALSE, warning=FALSE}
housing_prices_numeric <- housing_prices_tidy %>%
  select_if(is.numeric)

housing_prices_nonnumeric <- housing_prices_tidy %>%
  select_if(function(x) !is.numeric(x))

housing_prices_nonnumeric <- housing_prices_nonnumeric %>% 
  mutate(price = housing_prices_tidy$price)

housing_prices_nonnumeric %>% 
  distinct(grade)
```


```{r message=FALSE, warning=FALSE}
ggpairs(housing_prices_numeric)
ggpairs(housing_prices_nonnumeric)
```
strong correlation between price ~ sqft_living, bathrooms
some correlation between price ~ bedrooms
waterfront, renovated and grade all seem to have a relationship with price

```{r}
price_sqft_living <- lm(
  formula = price ~ sqft_living,
  data = housing_prices_tidy
)


price_sqft_living  
```

```{r}
autoplot(price_sqft_living)
summary(price_sqft_living)
```
residuals vs fitted: some evidence of a pattern, skewed
normal Q-Q: somewhat follows line
scale-location: funneling, some heteroscedasticity

R^2 = 49%


```{r}
price_bathrooms <- lm(
  formula = price ~ bathrooms,
  data = housing_prices_tidy
)
```

```{r}
autoplot(price_bathrooms)
summary(price_bathrooms)
```
Plots look ok.

R^2 accounts for around 26% of variance


```{r}
autoplot(lm(
  formula = price ~ bedrooms,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ grade,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ floors,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ floors,
  data = housing_prices_tidy
))

autoplot(lm(
  formula = price ~ waterfront,
  data = housing_prices_tidy
))


summary(lm(
  formula = price ~ waterfront,
  data = housing_prices_tidy
))
```

going with price_sqft_living

```{r}
housing_resid <- housing_prices_tidy %>% 
  add_residuals(model = price_sqft_living) %>% 
  select(-c(price, sqft_living))

housing_resid_numeric <- housing_resid %>%
  select_if(is.numeric)

housing_resid_nonnumeric <- housing_resid %>%
  select_if(function(x) !is.numeric(x))

housing_resid_nonnumeric <- housing_resid_nonnumeric %>% 
  mutate(resid = housing_resid$resid)
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_resid_numeric)
ggpairs(housing_resid_nonnumeric)
```
some relationship between residuals and waterfront, grade?

```{r}
autoplot(lm(
  formula = price ~ sqft_living + waterfront,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + waterfront,
  data = housing_prices_tidy
))
```
```{r}
autoplot(lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
))

price_living_grade <- lm(
  formula = price ~ sqft_living + grade,
  data = housing_prices_tidy
)
```

Going with grade, as it has a higher R^2

```{r}
anova(price_sqft_living, price_living_grade)
```

```{r}
housing_resid <- housing_prices_tidy %>% 
  add_residuals(model = price_living_grade) %>% 
  select(-c(price, sqft_living, grade))

housing_resid_numeric <- housing_resid %>%
  select_if(is.numeric)

housing_resid_nonnumeric <- housing_resid %>%
  select_if(function(x) !is.numeric(x))

housing_resid_nonnumeric <- housing_resid_nonnumeric %>% 
  mutate(resid = housing_resid$resid)
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_resid_numeric)
ggpairs(housing_resid_nonnumeric)
```
```{r}
autoplot(lm(
  formula = price ~ sqft_living + grade + waterfront,
  data = housing_prices_tidy
))

summary(lm(
  formula = price ~ sqft_living + grade + waterfront,
  data = housing_prices_tidy
))
```
__________________________________________________________________________________________

## Homework Review

```{r}
ggplot(housing_prices, aes(x = price)) +
  geom_histogram()
```

Thoughts at this point
  
  - House price is highly right skewed
  
Potential Candidates

Size of House (bedrooms, bathrooms, sqft)
Location (waterfront, view, lat, long, zip)
current state (yr_renovated, condition, grade)
age(yr_built)

Ultimate goal: build an explanatory model using multiple linear regression to explain variance in house price

Explore Data further (relationships between candidates, relationships between our outcome (price))

-> inform cleaning / preparation process

```{r}
head(housing_prices)

housing_prices %>% 
  count(waterfront)

housing_prices %>% 
  count(view) # Probably not worth including, because it's so heavily skewed

housing_prices %>% 
  count(condition)

housing_prices %>% 
  count(grade)

```
Overfitting 

You can fit the data you're currently looking at too well (model isn't general - just built for the one dataset)

Feature engineering
- Create has_been_renovated
- Drop a lot of columns (id, data, unuseful candidates)
- Maybe relevel some categorical columns (grades)

```{r}
housing_prices %>% 
  mutate(has_been_renovated = yr_renovated != 0) %>% 
  count(has_been_renovated)
```

```{r}
prices_trim <- housing_prices %>% 
  select(-c(id, date)) %>% 
  mutate(has_been_renovated = yr_renovated != 0,
         waterfront = as.logical(waterfront)) %>% 
  select(-yr_renovated)
```

```{r message=FALSE, warning=FALSE}
prices_trim %>% 
  slice_sample(prop = 0.8) %>% 
  select(price, bedrooms, bathrooms, sqft_living, sqft_lot, floors, sqft_basement, sqft_above) %>% 
  ggpairs()
```

Potential top house size candidate: sqft_living (looks linear and highly correlated)

```{r message=FALSE, warning=FALSE}
prices_trim %>% 
  slice_sample(prop = 0.8) %>% 
  select(price, waterfront, view, lat, long, zipcode) %>% 
  ggpairs()
```


Location not looking great, maybe waterfront, maybe latitude

```{r message=FALSE, warning=FALSE}
prices_trim %>% 
  slice_sample(prop = 0.8) %>% 
  mutate(grade = as.factor(grade)) %>% 
  select(price, has_been_renovated, condition, grade) %>% 
  ggpairs()
```

grade looks like a good candidate, doesn't look like enough houses have been renovated to see a noticeable difference.
We can only see a slight difference

```{r}
ggplot(prices_trim, aes(x = yr_built, y = price)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm")
```
yr_built isn't looking particularly related to house price

After exploration, the potentially best candidates for each quality (age, condition, location, size) were found to be:

+ sqft_living
+ latitude or waterfront
+ grade
+ yr_built

```{r message=FALSE, warning=FALSE}
prices_trim %>% 
  mutate(grade = as.factor(grade)) %>% 
  select(price, sqft_living, lat, waterfront, grade, yr_built) %>% 
  ggpairs()
```

Only big concern perhaps is the somewhat correlated yr_built and sqft_living (looks like houses have gotten larger over time)

```{r}
# create dataset with only candidates
prices_candidates <- prices_trim %>% 
  mutate(grade = as.factor(grade)) %>% 
  select(price, sqft_living, lat, waterfront, grade, yr_built)
  
```

# First predictor

```{r}
model_1a <- lm(price ~ sqft_living, data = prices_candidates)
model_1b <- lm(price ~ yr_built, data = prices_candidates)
model_1c <- lm(price ~ grade, data = prices_candidates)
```

```{r}
summary(model_1a)
summary(model_1b)
summary(model_1c)
```

```{r}
autoplot(model_1a)
autoplot(model_1b)
autoplot(model_1c)
```

After investigating the first predictor, model_1a (price ~ sqft_living) resulting in the highest value for R^2. It also showed evidence of non-linearity, 
heteroskedasticity and the residuals did not look to be normally distributed

After performing a log transformation on price, these problems decreased.

```{r}
model_1 <- lm(log(price) ~ sqft_living, data = prices_candidates)
```

# Second Predictor

```{r message=FALSE, warning=FALSE}
prices_candidates %>% 
  add_residuals(model_1, var = "resid") %>% 
  select(-sqft_living, -price) %>% 
  ggpairs()
```

```{r}
model_2a <- lm(log(price) ~ sqft_living + lat, data = prices_candidates)
model_2b <- lm(log(price) ~ sqft_living + waterfront, data = prices_candidates)
model_2c <- lm(log(price) ~ sqft_living + grade, data = prices_candidates)
```

```{r}
summary(model_2a)
summary(model_2b)
summary(model_2c)
```

```{r}
autoplot(model_2a)
autoplot(model_2b)
autoplot(model_2c)
```

While the diagnostics show an increase in heteroskedasticity, the residuals appear to show no clear trend and are normally distributed

Our current best model for house price is 

log(price) ~ sqft_living + lat


## Model Interpretation

The price of a house in King County can be explained by a combination of it's size (sqft of the living space) and its latitude (how far north it is)

e.g For a house that's 1910 sqft (living space) located at lat = 47.56

log(price) =  -62.56 +   (3.863e-04 * 1910)  +  (1.573 * 47.56)
           = 12.98971
    price  = e^(12.98971)    
           = 437884.3
           =~ 440,000
           
```{r}
model_2a
exp(12.98971) # exp is the reverse of log (ln)
```

