---
title: "Week 6 - Day 2 - Homework"
output: html_notebook
---

Question 1.
Load the data, clean_names() and explore it.
```{r}
library(tidyverse)

phones <- read_csv("data/20190928-items.csv") %>% 
  janitor::clean_names()
```

Question 2.
Find the brand with the highest numbers of phones in the dataset.
```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(num_phones = n()) %>% 
  arrange(desc(num_phones))
```

Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. 
Do you think the normal distribution provides a good model of these ratings?

I don't know if it's a good model - I dont really understand what the normal distribution is supposed to be showing. It looks like it lines up with the 
histogram, which i think is a good thing

```{r}
samsung_sd_mean <- phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(mean_rating = mean(rating),
         sd_rating = sd(rating))

phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = after_stat(density)), colour= "white") +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_sd_mean$mean_rating,
      sd = samsung_sd_mean$sd_rating
    ),
    col = "red"
  )
```

