---
title: "Week 6 - Day 2 - Homework"
output: html_notebook
---

Question 1.
Load the data, clean_names() and explore it.
```{r}
library(tidyverse)

phones <- read_csv("data/20190928-items.csv") %>% 
  janitor::clean_names()
```

Question 2.
Find the brand with the highest numbers of phones in the dataset.
```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(num_phones = n()) %>% 
  arrange(desc(num_phones))
```

Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. 
Do you think the normal distribution provides a good model of these ratings?

The normal distribution isn't a good model, as the data has two pretty even "peaks" - This tells us that the distribution can't fall into "normal" parameters

```{r}
samsung_sd_mean <- phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(mean_rating = mean(rating),
           sd_rating = sd(rating))

phones %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = after_stat(density)), colour= "white") +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_sd_mean$mean_rating,
      sd = samsung_sd_mean$sd_rating
    ),
    col = "red"
  ) 
```

Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. 
You calculated the mean() and sd() of your distribution in an earlier question. 
Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. 
Compare these proportions with those you expect for a normal distribution.

```{r}
samsung <- phones %>%
  filter(brand == "Samsung") %>% 
  select(rating)
samsung %>% 
  filter(rating >= samsung_sd_mean$mean_rating - samsung_sd_mean$sd_rating) %>%
  filter(rating <= samsung_sd_mean$mean_rating + samsung_sd_mean$sd_rating) %>%
  summarise(prop_within_1sd = n() / nrow(samsung))

samsung %>% 
  filter(rating >= samsung_sd_mean$mean_rating - (samsung_sd_mean$sd_rating * 2)) %>%
  filter(rating <= samsung_sd_mean$mean_rating + (samsung_sd_mean$sd_rating *2)) %>%
  summarise(prop_within_2sd = n() / nrow(samsung))

samsung %>% 
  filter(rating >= samsung_sd_mean$mean_rating - (samsung_sd_mean$sd_rating * 3)) %>%
  filter(rating <= samsung_sd_mean$mean_rating + (samsung_sd_mean$sd_rating *3)) %>%
  summarise(prop_within_3sd = n() / nrow(samsung))
```
These values don't fall in line with the Empirical 3-Sigma - They're probably not within a normal distribution
