---
title: "Week 6 - Day 3 - Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```
Task 1.
Load the data again, clean_names(), and familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>% 
  clean_names()
ames %>% 
head(5)
```
Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? 
If not, what problems do you find?
```{r}
ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram()
```

This distribution is not normal - it is heavily skewed to the right

Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.
```{r}
bootstrap_resample_100 <- ames %>% 
  rep_sample_n(size = 2930, replace = TRUE, reps = 100) %>% 
  summarise(mean_lot_area = mean(lot_area))

bootstrap_resample_100 %>% 
  ggplot(aes(x = mean_lot_area)) +
  geom_histogram(bins = 25, colour = "saddlebrown", fill = "green")
```
```{r}
# or using `infer`
infer_resample_100 <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 100, type = 'bootstrap') %>% 
  calculate(stat = 'mean') 

infer_resample_100 %>% 
  visualise(bins = 25)
```

Task 4.
Use your bootstrap distribution to calculate a 95%CI for mean(lot_area), 
and visualise it on the distribution
```{r}
infer_100_ci_95 <- infer_resample_100 %>% 
  get_ci(level = 0.95, type = "percentile")

infer_resample_100 %>% 
  visualise(bins = 25) +
  shade_ci(endpoints = infer_100_ci_95)
```

Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). 
Is it narrower or broader than the 95% CI? Does that make sense?
```{r}
infer_100_ci_99 <- infer_resample_100 %>% 
  get_ci(level = 0.99, type = "percentile")

infer_resample_100 %>% 
  visualise(bins = 25) +
  shade_ci(endpoints = infer_100_ci_99)

# It's broader as we are using a CI that covers more of the distribution - This makes sense
```

Task 6.
Calculate the point estimate of the mean(lot_area)
```{r}
infer_resample_100 %>% 
  summarise(mean = mean(stat))
```

EXT.

TASK 1

```{r}
# right idea, but using logical didn't work - using 1 for true and 0 for false seems to do it
year_built <- ames %>% 
  mutate(before_1920 = case_when(
    year_built < 1920 ~ 1,
    TRUE ~ 0
  ))

infer_resample_2000 <- year_built %>% 
  specify(response = before_1920) %>% 
  generate(reps = 2000, type = 'bootstrap') %>% 
  calculate(stat = 'mean') 

## All the rest goes here
```

