---
title: "Week 5 - Day 1 - Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
qb_revenue_breakdown <- CodeClanData::qb_revenue_breakdown
qb_monthly_sales <- CodeClanData::qb_monthly_sales
qb_competitors <- CodeClanData::qb_competitors
qb_device_data <- CodeClanData::qb_device_data
```

## MVP
# Part 1

Q1
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.

```{r}
qb_revenue_breakdown %>% 
  ggplot() +
  geom_bar(aes(x = Product, y= Revenue, fill = Year), stat = "identity")
```

Q2
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. 
This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}
qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount))
```

Q3
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount, group = Cashflow))
```

Q4
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.

```{r}
qb_competitors %>% 
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company))
```

Q5
Now show the sales from the four competitors as a line graph. 
Include an extra layer that shows the data points used to make the lines.

```{r}
qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, colour = Company)) +
  geom_line() +
  geom_point()
```

Q6
Now the company wants to compare the number of steps that their device counts vs. their competitors. 
Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. 
The data for this is in qb_device_data.

```{r}
qb_device_data %>% 
  ggplot() +
  geom_line(aes(x = hours, y = counts, colour = id)) +
  facet_grid(id~device, labeller = "label_both")
```

## Part 2

```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")
```


```{r}
qb_revenue_breakdown %>% 
  ggplot() +
  geom_bar(aes(x = Product, y= Revenue, fill = Year), stat = "identity") +
  labs(title = "Revenue by Product over 2018-2019") +
  scale_fill_manual(values = c(
    "2018" = "#F9A472",
    "2019" = "#BD7040")) +
  theme_bw() +
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
```

```{r}
qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount), colour = "#50434F")+
  scale_x_date(date_breaks = "1 month") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Monthly sales of KwikBit Unit 1")+
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
```

```{r}
library(scales)
```

```{r}
qb_monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>% 
  ggplot() +
  geom_line(aes(x = Date, y = Amount, group = Cashflow, colour = Cashflow))+ 
  scale_colour_manual(values = col_scheme) +
  scale_x_date(date_breaks = "1 month") +
  scale_y_continuous(breaks = c(1600, 2000, 2400, 2800)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = "Sales Amounts", title = "Monthly Cost and Total Revenue 2018/2019")+
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
  
```

```{r}
qb_competitors %>% 
  ggplot() +
  geom_area(aes(x = Year, y = Revenue, fill = Company)) +
  scale_fill_manual(values = col_scheme) +
  scale_y_continuous(labels = comma) +
  theme_bw() +
  labs(title = "Annual Sales of Rival Companies Products")+
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
  
```

```{r}
qb_competitors %>% 
  ggplot(aes(x = Year, y = Revenue, colour = Company)) +
  geom_line() +
  geom_point() +
  scale_colour_manual(values = col_scheme)+ 
  scale_y_continuous(labels = comma) +
  theme_bw() +
  labs(title = "Annual Sales of Rival Companies Products")+
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
```

```{r}
qb_device_data %>%
  ggplot() +
  geom_line(aes(x = hours, y = counts, colour = id)) +
  facet_grid(id ~ device, labeller = "label_both") +
  scale_colour_manual(values = col_scheme) +
  theme_bw() +
  labs(x = "Time in 24hr format",
       y = "Count of Steps",
       title = "Steps per Hour by ID and Device") +
  theme(axis.text = element_text(size = 12)) +
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) +
  theme(title = element_text(size = 14))
  
```

