---
title: "R Notebook"
output: html_notebook
---

```{r}
library(gtools)
library(tidyverse)
source('prob.R')
titanic <- read_csv("data/titanic.csv")
```
1.1 MVP

Titanic
```{r}
titanic <- titanic %>% 
  mutate(class = case_when(
    class == "3rd" ~ "passenger",
    class == "2nd" ~ "passenger",
    class == "1st" ~ "passenger",
    TRUE ~ "Crew")) 

titanic %>% 
  filter(class == "Crew") %>% # 890 rows
  filter(survived == "yes") # 211 rows

(211/890)*100
# crew had a 24% survival rate

```

```{r}
titanic %>% 
  filter(class == "passenger") %>%  # 1317 rows
  filter(survived == "yes") # 500 rows

(500/1317)*100
# Passengers had a 38% survival rate
```

Passengers had a higher survival rate 

1.2 
Probability Consolidation Questions

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}
(4/6)*100
# around 67%
```

Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?
```{r}
rolldie(3, nsides = 6)
# 216 outcomes
```
Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals (5, 6 or 7)? - 34
what is the probability of this event? - (34/1296) = 0.02623457
what assumptions do we apply in answering part ii? - We assume that the dice are not weighted, and that the randomisation is completely fair

```{r}
rolldie(4, nsides = 6) %>% 
  mutate(total = X1+X2+X3+X4) %>% # 1296 outcomes
  filter(total == 5 | total == 6 | total == 7) # 34 outcomes
```

Question 6.
If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?


```{r}
cards(jokers = FALSE) %>% 
  mutate(black_card = case_when(
    suit == "Club" ~ TRUE,
    suit == "Spade" ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  filter(black_card == TRUE) %>%  # drawing a black card = 26 outcomes
  filter(suit == "Spade") # card is a spade = 13 outcomes

# drawing spade in event of black card = 13/26 = 1/2
# drawing black card knowing it is a black card = 26/26 

(13/26)/(26/26)

```
I think
